Variable Composition of Microbial Biomass Affects the Accuracy of Microbial

### 2019-02-28 SI_code.Rmd
cleaning old scripts

@@

t.s1.1<-data.frame(Vmax=monod_r_results_par[,1],
                 Km=monod_r_results_par[,2],
                 CUE=monod_r_results_par[,3],
                 k=monod_r_results_par[,4])
row.names(t.s1.1)<-c("All", "Broth", "Glass", "Wool",
                    "Celluloze", "Glucose",
                    "Broth - Celluloze", "Broth - Glucose",
                    "Glass - Celluloze", "Glass - Glucose",
                    "Wool - Celluloze", "Wool - Glucose")

@@

t.s2.1<-data.frame(Vmax=mend_r_results_par[,1],
                 Km=mend_r_results_par[,2],
                 CUE=mend_r_results_par[,3],
                 mr=mend_r_results_par[,4])
row.names(t.s2.1)<-c("All", "Broth", "Glass", "Wool",
                    "Celluloze", "Glucose",
                    "Broth - Celluloze", "Broth - Glucose",
                    "Glass - Celluloze", "Glass - Glucose",
                    "Wool - Celluloze", "Wool - Glucose")

@@

t.s3.1<-data.frame(Vmax=deb_r_results_par[,1],
                 Km=deb_r_results_par[,2],
                 mo=deb_r_results_par[,3],
                 f=deb_r_results_par[,4],
                 Yu=deb_r_results_par[,5])
row.names(t.s3.1)<-c("All", "Broth", "Glass", "Wool",
                    "Celluloze", "Glucose",
                    "Broth - Celluloze", "Broth - Glucose",
                    "Glass - Celluloze", "Glass - Glucose",
                    "Wool - Celluloze", "Wool - Glucose")

@@

t.s4.1<-data.frame(Name=rep(c("All", "Broth", "Glass", "Wool",
                    "Celluloze", "Glucose",
                    "Broth - Celluloze", "Broth - Glucose",
                    "Glass - Celluloze", "Glass - Glucose",
                    "Wool - Celluloze", "Wool - Glucose"), each =2),
                   Parameter=rep(c("Protein", "DNA"), times=12),
                   Vmax=monod_all_results_par[,1],
                   Km=monod_all_results_par[,2],
                   CUE=monod_all_results_par[,3],
                   k=monod_all_results_par[,4],
                   conv=monod_all_results_par[,5])

@@

t.s5.1<-data.frame(Name=rep(c("All", "Broth", "Glass", "Wool",
                    "Celluloze", "Glucose",
                    "Broth - Celluloze", "Broth - Glucose",
                    "Glass - Celluloze", "Glass - Glucose",
                    "Wool - Celluloze", "Wool - Glucose"), each =2),
                   Parameter=rep(c("Protein", "DNA"), times=12),
                   Vmax=mend_all_results_par[,1],
                   Km=mend_all_results_par[,2],
                   CUE=mend_all_results_par[,3],
                   mr=mend_all_results_par[,4],
                   conv=mend_all_results_par[,5])

@@

t.s6.1<-data.frame(Name=c("All", "Broth", "Glass", "Wool",
                    "Celluloze", "Glucose",
                    "Broth - Celluloze", "Broth - Glucose",
                    "Glass - Celluloze", "Glass - Glucose",
                    "Wool - Celluloze", "Wool - Glucose"),
                   Vmax=deb_all_results_par[,1],
                   Km=deb_all_results_par[,2],
                   m0=deb_all_results_par[,3],
                   f=deb_all_results_par[,4],
                   Yu=deb_all_results_par[,5],
                   fpr=deb_all_results_par[,6],
                   fps=deb_all_results_par[,7],
                   fds=deb_all_results_par[,8])

>>>>

```
##Statistical analysis
###Respiration
Cumulative respiration is calculated from the measured respiration rate using the local polynomial regression.

@@

t.s1.1<-data.frame(Vmax=monod_r_results_par[,1],
                 Km=monod_r_results_par[,2],
                 CUE=monod_r_results_par[,3],
                 k=monod_r_results_par[,4])
row.names(t.s1.1)<-c("All", "Broth", "Glass", "Wool",
                    "Cellobiose", "Glucose",
                    "Broth - Cellobiose", "Broth - Glucose",
                    "Glass - Cellobiose", "Glass - Glucose",
                    "Wool - Cellobiose", "Wool - Glucose")

@@

t.s2.1<-data.frame(Vmax=mend_r_results_par[,1],
                 Km=mend_r_results_par[,2],
                 CUE=mend_r_results_par[,3],
                 mr=mend_r_results_par[,4])
row.names(t.s2.1)<-c("All", "Broth", "Glass", "Wool",
                    "Celluloze", "Glucose",
                    "Broth - Cellobiose", "Broth - Glucose",
                    "Glass - Cellobiose", "Glass - Glucose",
                    "Wool - Cellobiose", "Wool - Glucose")

@@

t.s3.1<-data.frame(Vmax=deb_r_results_par[,1],
                 Km=deb_r_results_par[,2],
                 mo=deb_r_results_par[,3],
                 f=deb_r_results_par[,4],
                 Yu=deb_r_results_par[,5])
row.names(t.s3.1)<-c("All", "Broth", "Glass", "Wool",
                    "Cellobiose", "Glucose",
                    "Broth - Cellobiose", "Broth - Glucose",
                    "Glass - Cellobiose", "Glass - Glucose",
                    "Wool - Cellobiose", "Wool - Glucose")

@@

t.s4.1<-data.frame(Name=rep(c("All", "Broth", "Glass", "Wool",
                    "Cellobiose", "Glucose",
                    "Broth - Cellobiose", "Broth - Glucose",
                    "Glass - Cellobiose", "Glass - Glucose",
                    "Wool - Cellobiose", "Wool - Glucose"), each =2),
                   Parameter=rep(c("Protein", "DNA"), times=12),
                   Vmax=monod_all_results_par[,1],
                   Km=monod_all_results_par[,2],
                   CUE=monod_all_results_par[,3],
                   k=monod_all_results_par[,4],
                   conv=monod_all_results_par[,5])

@@

t.s5.1<-data.frame(Name=rep(c("All", "Broth", "Glass", "Wool",
                    "Cellobiose", "Glucose",
                    "Broth - Cellobiose", "Broth - Glucose",
                    "Glass - Cellobiose", "Glass - Glucose",
                    "Wool - Cellobiose", "Wool - Glucose"), each =2),
                   Parameter=rep(c("Protein", "DNA"), times=12),
                   Vmax=mend_all_results_par[,1],
                   Km=mend_all_results_par[,2],
                   CUE=mend_all_results_par[,3],
                   mr=mend_all_results_par[,4],
                   conv=mend_all_results_par[,5])

@@

t.s6.1<-data.frame(Name=c("All", "Broth", "Glass", "Wool",
                    "Cellobiose", "Glucose",
                    "Broth - Cellobiose", "Broth - Glucose",
                    "Glass - Cellobiose", "Glass - Glucose",
                    "Wool - Cellobiose", "Wool - Glucose"),
                   Vmax=deb_all_results_par[,1],
                   Km=deb_all_results_par[,2],
                   m0=deb_all_results_par[,3],
                   f=deb_all_results_par[,4],
                   Yu=deb_all_results_par[,5],
                   fpr=deb_all_results_par[,6],
                   fps=deb_all_results_par[,7],
                   fds=deb_all_results_par[,8])
